Distance Sampling in \proglang{R}

### 2015-11-24 paper.Rmd
Eric comments addressed up to "Detection functions"

_before getting too deep into detection functions, would be nice to describe the 2-stage nature; adjust counts by detectability to get $\hat{N_c}$ then scale up $\hat{N_c}$ to get $\hat{N}$_

Census-type surveys (quadrat or strip transects assuming perfect detectability within strips or quadrats) are inefficient (requiring considerable field effort) and we should expect that not all objects (animals, plants, dung, etc) can be observed. Accounting for imperfect detectability is an important consideration when obtaining accurate estimates of abundance [@LahozMonfort:2013bg]. Using the extra information gained by recording distance from the sampler to the observation, it is possible to model detectability. Because we expect detectability to decrease with increasing distance from the sampler, we model detectability as a function of distance (plus perhaps other covariates, see below).

@@

For both points and lines, once the geometry of the sampler _likely spell out geom of sampler, or note it specification is forthcoming_ has been taken into account, the histogram of distances should show a decreasing number of observations with increasing distance from the sampler. For line transects we expect objects to be distributed unformly with respect to distance from the line and what makes our histogram decrease is the detectability. For point transects, we recognise that as distance from the point increases, the area of the circle encompassed increases with distance squared; hence the number of objects available to be detected is a linearly increasing function of distance from the point.

>>>>

Census-type surveys (quadrat or strip transects assuming perfect detectability within strips or quadrats) are inefficient (requiring considerable field effort) and we should expect that not all objects (animals, plants, dung, etc) can be observed. Accounting for imperfect detectability is an important consideration when obtaining accurate estimates of abundance [@LahozMonfort:2013bg]. Using the extra information gained by recording distance from the sampler to the observation, it is possible to model detectability. Because we expect detectability to decrease with increasing distance from the sampler, we model detectability as a function of distance (plus perhaps other covariates, see below). We use the probabilities of detection calculated from the detection function to estimate an abundance for the area covered by the survey, which we then scale-up to the study region of interest.

@@

For both points and lines, once the geometry of the sampler (see "Detection functions") has been taken into account, the histogram of distances should show a decreasing number of observations with increasing distance from the sampler. For line transects we expect objects to be distributed unformly with respect to distance from the line and what makes our histogram decrease is the detectability. For point transects, we recognise that as distance from the point increases, the area of the circle encompassed increases with distance squared; hence the number of objects available to be detected is a linearly increasing function of distance from the point.

### 2015-11-24 paper.tex
Eric comments addressed up to "Detection functions"

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\emph{before getting too deep into detection functions, would be nice to
describe the 2-stage nature; adjust counts by detectability to get
\(\hat{N_c}\) then scale up \(\hat{N_c}\) to get \(\hat{N}\)}

Census-type surveys (quadrat or strip transects assuming perfect
detectability within strips or quadrats) are inefficient (requiring
considerable field effort) and we should expect that not all objects
(animals, plants, dung, etc) can be observed. Accounting for imperfect
detectability is an important consideration when obtaining accurate
estimates of abundance (Lahoz-Monfort, Guillera-Arroita, and Wintle
2013). Using the extra information gained by recording distance from the
sampler to the observation, it is possible to model detectability.
Because we expect detectability to decrease with increasing distance
from the sampler, we model detectability as a function of distance (plus
perhaps other covariates, see below).

@@

For both points and lines, once the geometry of the sampler \emph{likely
spell out geom of sampler, or note it specification is forthcoming} has
been taken into account, the histogram of distances should show a
decreasing number of observations with increasing distance from the
sampler. For line transects we expect objects to be distributed unformly
with respect to distance from the line and what makes our histogram
decrease is the detectability. For point transects, we recognise that as
distance from the point increases, the area of the circle encompassed
increases with distance squared; hence the number of objects available
to be detected is a linearly increasing function of distance from the
point.

>>>>

@@

Census-type surveys (quadrat or strip transects assuming perfect
detectability within strips or quadrats) are inefficient (requiring
considerable field effort) and we should expect that not all objects
(animals, plants, dung, etc) can be observed. Accounting for imperfect
detectability is an important consideration when obtaining accurate
estimates of abundance (Lahoz-Monfort, Guillera-Arroita, and Wintle
2013). Using the extra information gained by recording distance from the
sampler to the observation, it is possible to model detectability.
Because we expect detectability to decrease with increasing distance
from the sampler, we model detectability as a function of distance (plus
perhaps other covariates, see below). We use the probabilities of
detection calculated from the detection function to estimate an
abundance for the area covered by the survey, which we then scale-up to
the study region of interest.

@@

For both points and lines, once the geometry of the sampler (see
``Detection functions'') has been taken into account, the histogram of
distances should show a decreasing number of observations with
increasing distance from the sampler. For line transects we expect
objects to be distributed unformly with respect to distance from the
line and what makes our histogram decrease is the detectability. For
point transects, we recognise that as distance from the point increases,
the area of the circle encompassed increases with distance squared;
hence the number of objects available to be detected is a linearly
increasing function of distance from the point.
